---
title: "Delta Price Scrapper"
author: "Lex Liu"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`deltaprice` package aims to scrape Delta Airline ticket price. Given a list of departure and return dates, this package will help you collect ticket prices. This package aims to help people plan the most budget trip. Also, this package works as a starter code for anyone thinking to scrape a dynamic webpage using `Selenium` in `R`. 

## Dependencies

Before running `RSelenium`, the following is required:

- install a version of [java SE]("https://www.oracle.com/technetwork/java/javase/overview/index.html") on your machine
- download a [standalone selenium server]("https://bit.ly/2TlkRyu")

When you have the items above ready, run the following command in the terminal prior to scraping. Remember to **navigate** to the folder where the .jar file sits and **replace 3.9.1** with the version on your machine. Also, the selenium server above works for most of the mordern browsers, and if it is not the case for you, visit [Selenium]("https://www.seleniumhq.org/") for more options.
```
    java -jar selenium-server-standalone-3.9.1.jar
```

## Example

```
library(RSelenium)
library(deltaprice)
remDr <- remoteDriver(browserName="chrome", remoteServerAddr="localhost", port=4444L)
remDr$open()
dateGrid <- data.frame("depart"=c("1/1/2019", "1/1/2019", "1/2/2019", "1/2/2019"),           
                "return"=c("1/3/2019","1/4/2019","1/3/2019","1/4/2019"))
price <- main("LAX", "JFK", dateGrid1, remDr)
```

## Visualization

You can visualize the results. We will be using the dataset included in the package for demo.
```{r echo=FALSE, fig.height=3.94, fig.width=7, message=FALSE, warning=F}
data("pricedf", package="deltaprice")
library(ggplot2)
ggplot(pricedf, aes(departure, price, fill=departure)) + geom_violin(scale="area")
```

```{r echo=FALSE, fig.height=3.94, fig.width=7, message=FALSE, warning=FALSE}
data("pricedf", package="deltaprice")
library(ggplot2)
ggplot(pricedf, aes(price)) + geom_histogram() + facet_grid(departure ~ return)
```
